---
title: "Final Project Abalysis"
author: "Blinda Tian"
date: "12/4/2020"
output:
  word_document: default
  html_document: default
---


#  type of analysis
final <- rbind(sse_new,snp)
write.csv(file="~/Desktop/final.csv", final)
```{r merge}
final <- read.csv("~/Desktop/final.csv")
```

# The Mean Absolute Error (MAE)
measures the average magnitude of the errors in a set of predictions
Mean Squared Error (NMSE)
# assumption
parallel trend
```{r}

# parallel trend
# Group is not affected by news (parallel trend on no vaccine news)
plot(final$Adj.Close[final$News==0&final$Country_treat==1], type="l",col="red",ylim= c(3100,3500),main="No News day",xlab="Time Events",ylab="Index")
lines(final$Adj.Close[final$News==0&final$Country_treat==0],col="blue")



# after treatment; affected by news
plot(final$Adj.Close[final$News==1&final$Country_treat==1], type="l",col="red",ylim= c(3100,3700))
lines(final$Adj.Close[final$News==1&final$Country_treat==0],col="blue")



```


# DID model
From my data, I would wish to know whether U.S investors that observe vaccine news will  an increase in buying than Chinese investors;
 test whether the time effect is different when you intervene compared with when you don't.



Time is binary (0,1) where 0 is no vaccine news and 1 was days that have vaccine news. 
Country training is also binary, where 0 is a Chinses stock index and 1 is U.S stock index Income is continuous variable (index)

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)         3270.14      24.11 135.658  < 2e-16 ***
News                  22.64      32.50   0.697  0.49051    
Country_treat        115.21      34.09   3.379  0.00176 ** 
News:Country_treat   -58.46      45.97  -1.272  0.21160   
```{r set varibles}

# model DID

final$Diff_ab <- abs(final$Diff)
didreg <- lm( final$Diff_ab ~   News*Country_treat, data = final)
summary(didreg)




# validation

mean(didreg$residuals)
plot(didreg$residuals)
acf(didreg$residuals)
lmtest::dwtest(didreg) # reject (there is a autocorrelation)
#No perfect multicollinearity
library(car)
vif(didreg)
plot(didreg,2) # 21 23 5

final2 <- final[-c(21,23,5),]

# remove outliers
didreg <- lm( final2$Diff_ab ~   News*Country_treat, data = final2) # less SE 
summary(didreg)








```




# simulation
```{r}
plot(didreg$fitted.values)
```


